Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-27 paper/ms.tex
update ms

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\caltech}{Department of Astronomy, MC 249-17, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\mitkavli}{MIT Kavli Institute and Department of Physics, 77 Massachusetts Avenue, Cambridge, MA 02139}
\newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}
\newcommand{\princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
\newcommand{\esa}{European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands}

@@

@@

@@

\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
%
\author{Saul~Rappaport}
\affiliation{\mitkavli}

\author[0000-0001-6381-515X]{Luisa M. Rebull}
\affiliation{\caltech}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS short-cadence data collected between July~2018
  and Sep~2022.  Our search of \nstarssearched\ K and M dwarfs with
  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
  of these discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc) examples of this
  class of object known, as well as the most massive
  ($\approx$0.6-0.8\,$M_\odot$) and oldest ($\approx$200\,Myr).  A few
  objects are outliers among outliers; LP 12-502 for instance shows a
  recurring ``dip complex'' with a period and total duration that are
  fixed over more than 1{,}000 cycles, but which in detail showed
  anywhere from four to eight local minima per cycle, and at times
  displayed distinct superposed periods simultaneously.  Broadly
  speaking, we find that none of the CQVs maintain a fixed light curve
  shape over timescales of more than a few hundred cycles, and we
  revisit the arguments for why transient corotating material is the
  most viable explanation.  We expect that our sample will facilitate
  future efforts aimed at connecting these objects to the broader
  contexts of star, disk, and exoplanet evolution. 
  %For instance, if the transiting material is dust, then the rate of
  %dip evolution implies that of order an asteroid belt's worth of mass
  %passes through these structures over their lifetime of
  %$\approx$$10^8$ years.
\end{abstract}

@@

The dust clump and prominence hypotheses seem most plausible.  They
are qualitatively similar, except that one invokes opacity from dust,
while the other invokes opacity from gas, likely bound-free
transitions in hydrogen or perhaps a molecular opacity.  The screen
scenario seems inconsistent with the degree of observed periodicity,
the lack of infrared excess, and the observed lifetime of CQVs
extending an order of magnitude longer than the $\approx$$10^7$ year
timescale typically quoted for primordial disk dispersal.  However,
unambiguous evidence in support of any one scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line absorption as a function of cycle phase,
similar to observations made in systems such as AB~Dor \citep[see the
review by][]{1999ASPC..158..146C}.

@@

In this work, we aim to find bright and nearby CQVs, since these
objects will be the most amenable to detailed photometric and
spectroscopic analyses.  To do this, we use 120-second cadence data
acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55; Cycles
1-4).  We present our search methods in Section~\ref{sec:methods}, and
the properties of the resulting CQV catalog in
Section~\ref{sec:results}.  The evolution of many CQVs over a two-year
baseline is described in Section~\ref{sec:evoln}, including a
deep-dive into LP 12-502.  We describe a few implications in
Section~\ref{sec:discussion}, and conclude in
Section~\ref{sec:conclusion}.

@@

Planet occurrence rate studies from Kepler have shown that high-mass
M  dwarfs have $\approx$0.1 planets per star with sizes between
1-4\,$R_\oplus$ and orbital periods within 3 days
\citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
planets per star for planets with 1-4\,$R_\oplus$ and $P$$<$10\,days.
Extrapolating to all small close-in planets, with say
0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
average one planet per M dwarf.  TRAPPIST-1b ($P$=1.5\,days) is an
example of this type of planet, in orbit around a 0.08\,$M_\odot$ star
\citep{2017Natur.542..456G}.

In the context of planet formation, the stopping location for the
inner-most planet is set by the location of the protoplanetary disk's
truncation radius \citep{2018haex.bookE.142I}.  Although this disk
truncation radius is defined by equating the magnetic pressure from
the stellar magnetosphere with the ram pressure form the inflowing
gas, it also tends to roughly coincide with the Keplerian corotation
radius \citep{2016ARA&A..54..135H}.  Within models that have compact
multiplanet resonant chains migrate inward due to gas drag, the
inner-most planets arrive within $\approx$5-10 stellar radii before
the disk becomes depleted.

In this context, it is tempting to try to interpret features of the
CQV light curves in terms of the possible presence of close-in
exoplanets, or even planetesimals, that are expected to exist in
abundance around these stars.  Rocky planets this young could have
molten global magma oceans analogous to those that existed on the
Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
undergoing significant outgassing and atmospheric escape.  However,
although it is {\it a priori} plausible that close-in rocky planets or
planetesimals could serve as a possible source of material for the
clouds, any evidence in support of such a picture currently seems
ambiguous at best.

In systems like LP 12-502, the observed dip depth variations would
necessarily drive one toward a picture of a disintegrating
planetesimal swarm, rather than just a single planetesimal.  
While the number of free parameters in this type of model is somewhat
dizzying, we have no right to believe that nature need be simple.
The need for a swarm rather than just one launching body would
be driven by the observation that we see dips appear and disappear at
many {\it different phases}, but with roughly the same period.
The observed changing dip depths in response to flares would be
understood through the planetesimal outflow rates being stalled by
changes in the local magnetic field or coronal plasma density.
The sizes of these purported planetesimals would need to be $\lesssim
1$\,$R_\oplus$, based on the non-detections of their transits,
analogous to e.g.  K2-22 \citep{2015ApJ...812..112S} or KOI-2700
\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
belt for instance span hundreds of meters to a few kilometers.

The planetesimal swarm model would predict that certain orbital phases
would produce recurrent dips if observed over sufficiently long
timescales, since the launching planetesimal would be massive enough
to remain in orbit, and similar to say K2-22 would stochastically
eject material.  While the regularity of the dip phases of LP~12-502
over the existing baseline (Figure~\ref{fig:lp2}) might agree with
this prediction, for most other CQVs (Figure~\ref{fig:evoln}) the data
seem to be in tension with this expectation.

There are a few additional problems for the idea of a disintegrating
planetesimal swarm.  First, many of the dips show asymmetries in the
wrong direction relative to the naive expectation of a trailing comet
tail.  Invoking non-exponentially decaying dust distributions as a
function of azimuth might be one way out of this, but such an idea
would need stronger theoretical footing.  Dynamical stability would be
a separate concern: in a model in which any new dip is ``explained''
by invoking a new planetesimal, one might eventually pack the
corotation radius to a degree where instability over short timescales
would be guaranteed.

It is certainly possible that exoplanets or exoplanetesimals could end
up being connected to the CQV phenomenon, for instance as a possible
source of dust through collisions at greater separations from the
star.  However for the time being, none of the CQVs that we have
studied in this work seem to show clear evidence for this type of
origin scenario.

@@

\begin{figure}[!t]
	\begin{center}
		\centering
		%\includegraphics[width=0.9\textwidth]{f8.pdf}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f8a.pdf}
		}

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f8b.pdf}
		}
		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection}.  HD~37776 and HD~64740 (right column) are
      magnetic B stars with field geometries dominated by high order
      multipoles.
			Here, we compare their phased TESS light curves against the
			``best-matching'' CQV light curves (left column), selected by eye from
			Figure~\ref{fig:cqvs}.
      Stellar masses rounded to one significant figure are given
      in the lower right of each panel; the star, TESS sector, and
      period are listed in the title.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

One possible argument against the connection between CQVs and the
$\sigma$~Ori~E analogs is that the light curve of $\sigma$~Ori~E is
much simpler than those in Figure~\ref{fig:cqvs}, with only two broad
local minima, and one ``hump'' \citep{2005ApJ...630L..81T}.  Within
the model proposed by Townsend et al., this is tied to the star's
magnetic field, which to first-order is reasonably described as a
dipole, similar to most other magnetic B stars
\citep{2009ARA&A..47..333D}.  This approximation fits the qualitative
behavior of not only the broadband light curves, but also the
line-profile variations seen in hydrogen, helium, and carbon
\citep{2012MNRAS.419..959O}.

Two exceptions to the rule of ``simple field topologies for magnetic
B stars'' are HD~37776 and HD~64740, which are B stars that were
previously known from spectropolarimetry in the 2000s-2010s to have
field geometries dominated by high order multipoles
\citep{2011ApJ...726...24K}.  In a review of the literature, we
learned that recent TESS light curves of these two B stars appear
surprisingly similar to the CQV light curves
\citep{2020pase.conf...46M}.  Figure~\ref{fig:bstar} shows the phased
TESS light curves for the two outlying magnetic B stars, with by-eye
``best matching'' CQVs shown for comparison.  The number of dips per
cycle, the shapes of the dips, and the dip depths relative to the
sinusoidal envelope, all seem to be quite similar.  If this connection
is taken seriously, the implication would be that the
highly-structured M dwarf light curves imply multipolar magnetic
fields -- since it is the complex fields which are the defining
characteristic of these two B stars, relative to other known magnetic
B stars like $\sigma$~Ori~E.  
This is consistent with the non-axisymmetric topologies that have been
reported in a small number of M dwarfs for which Zeeman Doppler
Imaging is technically feasible 
\citep[see the recent review by][]{2021A&ARv..29....1K}.

The physical similarity between the B stars and the M dwarfs is
presumably the existence of a ``centrifugal magnetosphere'': in other
words, they both satisfy the condition $R_{\rm A} > R_{\rm cr}$, for
$R_{\rm A}$ the Alfv\'en radius.
% TODO : qualitiatively explain, and cite Petit+2013
In the converse case of a ``dynamical'' magnetosphere...
{\bf todo: summarize Petit2013}
%FIXME TODO
%FIXME TODO
%FIXME TODO
{\bf
LGB todo: make the connection to Jupiter-Io magnetosphere, and that
plasma torus too
}

@@

\begin{enumerate}[leftmargin=*]
	%
	\item CQVs are quasiperiodic.  The mean periods remain fixed over the
		$>$1{,}000-cycle baseline of available observations; but the light curve shapes
		always evolve (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often but not
    exclusively linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay can also occur.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
  \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
    200\,Myr, based on the one CQV we found in the Carina Near
    moving group (TIC~294328887; $\approx$200\,Myr).  The lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    lifetime of the phenomenon is likely limited to the first few
    hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item While the majority of detected CQVs have masses of
    0.1-0.5\,$M_\odot$, the upper mass limit for the CQV phenomenon
    might extend into the K dwarf regime ($<$$0.8$\,$M_\odot$).
    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
    $\approx$0.6 solar masses, are the two massive outliers
    (Section~\ref{subsec:extreme}), and we encourage additional
    scrutiny of these objects in future work.
  %
    \item Surprising analogs to the M  and K dwarf CQVs exist in
    magnetic B stars, but only those with multipolar field topologies.
    This suggests that the CQV dips and warps are strongly sculpted
    by the stellar magnetic fields, which would also be multipolar.
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
	APPROPRIATE)}
LGB~and RJ conceived the project and executed the
dip-based and Fourier-based searches, respectively.
LGB~drafted the initial manuscript, and performed the cluster
membership, SED, and variability analyses.
SR and RJ vetted the results from the Fourier search.
LAH advised on project scope and experiment design.
G\'AB acquired and maintained the servers used to run the dip-finding
pipeline.
GRR is an architect of the TESS mission.
All authors assisted in manuscript revision.

>>>>

%%%%%%%%%%%%%%%%
% INSTITUTIONS %
%%%%%%%%%%%%%%%%
\newcommand{\caltech}{Department of Astronomy, MC 249-17, California Institute of Technology, Pasadena, CA 91125, USA}
\newcommand{\mitkavli}{MIT Kavli Institute and Department of Physics, 77 Massachusetts Avenue, Cambridge, MA 02139}
\newcommand{\berkeley}{Astronomy Department, University of California, Berkeley, CA 94720, USA}
\newcommand{\princeton}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08540, USA}
\newcommand{\esa}{European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands}
\newcommand{\howard}{Department of Physics and Astronomy, Howard University, Washington DC, 20059}
\newcommand{\goddard}{Center for Research and Exploration in Space Science and Technology, and X-ray Astrophysics Laboratory, NASA/GSFC, Greenbelt, MD 20771, USA}

@@

\author{Saul~Rappaport}
\affiliation{\mitkavli}

@@

\author[0000-0003-4062-0776]{Alexandre David-Uraz}
\affiliation{\howard}
\affiliation{\goddard}

@@

\author{-----SUGGESTED CONTRIBUTORS, PENDING DISCUSSION, COMMENTS, ANALYSES, ETC-----}
%
\author[0000-0001-6381-515X]{Luisa M. Rebull}
\affiliation{\caltech}

@@

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS short-cadence data collected between July~2018
  and Sep~2022.  Our search of \nstarssearched\ K and M dwarfs with
  $T$$<$16 and $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most
  of these discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc) examples of this
  class of object known, as well as the most massive
  ($\approx$0.6-0.8\,$M_\odot$) and the oldest ($\approx$200\,Myr).  A few
  objects are outliers among outliers; LP 12-502 for instance shows a
  recurring ``dip complex'' with a period and total duration that are
  fixed over more than 1{,}000 cycles, but which in detail contains
  anywhere from four to eight local minima per cycle, and at times
  displays distinct superposed periods simultaneously.  Broadly
  speaking, we find that none of the CQVs maintain a fixed light curve
  shape over timescales of more than a few hundred cycles, and we
  revisit the arguments for why transient corotating material is the
  most viable explanation.  We expect that our sample will facilitate
  future efforts aimed at connecting these objects to the broader
  contexts of star, disk, and perhaps even exoplanet evolution. 
  %For instance, if the transiting material is dust, then the rate of
  %dip evolution implies that of order an asteroid belt's worth of mass
  %passes through these structures over their lifetime of
  %$\approx$$10^8$ years.
\end{abstract}

@@

The dust clump and prominence hypotheses seem most plausible.  They
are qualitatively similar, except that one invokes opacity from dust,
while the other invokes opacity from gas, likely bound-free
transitions in hydrogen or perhaps a molecular opacity.  The screen
scenario seems inconsistent with the degree of observed periodicity,
the lack of infrared excess, and the observed lifetime of CQVs
extending an order of magnitude longer than the $\approx$$10^7$ year
timescale typically quoted for primordial disk dispersal.  However,
unambiguous evidence in support of any one scenario has yet to be
acquired.  Such evidence might include a spectroscopic detection of
silicate 10\,$\mu$m dust absorption during a dip, or perhaps detection
of transient Balmer-line excesses as a function of cycle phase,
similar to observations made in systems such as AB~Dor
\citep[see][]{1999ASPC..158..146C} or PTFO 8-8695 \citep{2016ApJ...830...15J}.

@@

In this work, we aim to find bright and nearby CQVs, since these
objects will be the most amenable to detailed photometric and
spectroscopic analyses.  To do this, we use 120-second cadence data
acquired by TESS between July~2018 and Sep~2022 (Sectors 1-55; Cycles
1-4).  We present our search methods in Section~\ref{sec:methods}, and
the properties of the resulting CQV catalog in
Section~\ref{sec:results}.  The evolution of many CQVs over a two-year
baseline is described in Section~\ref{sec:evoln}, including a
deep-dive into LP 12-502.  We discuss a few implications in
Section~\ref{sec:discussion}, and conclude in
Section~\ref{sec:conclusion}.

@@

Close-in planets are common around M-dwarfs;
studies from Kepler have shown that high-mass
M  dwarfs have $\approx$0.1 planets per star with sizes between
1-4\,$R_\oplus$ and orbital periods within 3 days
\citep{2015ApJ...807...45D}.  The number increases to $\approx$0.7
planets per star considering planets out to $P$$<$10\,days.
Extrapolating to all small close-in planets with say
0.1-4\,$R_\oplus$ and within 10 days, it is reasonable to expect on
average one close-in planet per M dwarf.  
%TRAPPIST-1b ($P$=1.5\,days) is an
%example of this type of planet, orbiting around a 0.08\,$M_\odot$ star
%\citep{2017Natur.542..456G}.

In the context of planet formation, the stopping location for the
inner-most planet is set by the location of the protoplanetary disk's
truncation radius \citep{2018haex.bookE.142I}.  Although this disk
truncation radius is defined by equating the magnetic pressure from
the stellar magnetosphere with the ram pressure form the inflowing
gas, it also tends to roughly coincide with the Keplerian corotation
radius \citep{2016ARA&A..54..135H}.  Within models that have compact
multiplanet resonant chains migrating inward due to gas drag, the
inner-most planets therefore arrive at $\approx$5-10 stellar radii before
the disk becomes depleted.

Given this context, it is tempting to try to interpret features of the
CQV light curves in terms of the possible presence of close-in
exoplanets, or even planetesimals.  Rocky planets this young could have
molten global magma oceans analogous to those that existed on the
Earth and Moon \citep[see][]{2022arXiv220310023L}, and thus might be
undergoing significant outgassing and atmospheric escape.  The system
would then be analogous to the Jupiter-Io plasma torus \citep[e.g.][]{1980JGR....85.1171N}, with a similar rotation
period for the primary and orbital period for the secondary,
but magnetic fields stronger by a factor of $\approx$1{,}000.
While this type of configuration is {\it a priori} plausible,
any evidence in support of such a picture currently seems
ambiguous at best.

In systems like LP 12-502, the observed dip depth variations would
necessarily drive one toward a picture of a disintegrating
planetesimal swarm, rather than just a single planetesimal.  
%While the number of free parameters in this type of model is somewhat
%dizzying, we have no right to believe that nature need be simple.
The need for a swarm rather than just one launching body would
be driven by the observation that we see dips appear and disappear at
many {\it different phases}, but with roughly the same period.
The observed changing dip depths in response to flares would be
understood through the planetesimal outflow rates being stalled by
changes in the local magnetic field or coronal plasma density.
The sizes of these purported planetesimals would need to be $\lesssim
1$\,$R_\oplus$, based on the non-detections of their transits,
analogous to e.g.  K2-22 \citep{2015ApJ...812..112S} or KOI-2700
\citep{2014ApJ...784...40R}.  Typical sizes of bodies in the asteroid
belt for instance span hundreds of meters to a few kilometers.

There are at least three problems with the idea of a disintegrating
planetesimal swarm.
First, this model would predict that certain orbital phases
would produce recurrent dips if observed over sufficiently long
baselines, because the launching planetesimal would be massive enough
to remain in orbit, while stochastically
ejecting material.  An analogous system might be K2-22.
For most CQVs (Figure~\ref{fig:evoln}), the data
seem to be in tension with this expectation.
A second issue is that many of the dips show asymmetries in the
wrong direction relative to the naive expectation of a trailing comet
tail.  Invoking non-exponentially decaying dust distributions as a
function of azimuth might be one way out of this, but such an idea
lacks firm theoretical footing.  Finally, dynamical stability is a concern:
in a model in which any new dip is ``explained''
by invoking a new planetesimal, one might eventually pack the
corotation radius to a degree where instability over short timescales
would be guaranteed.

It is certainly possible that exoplanets or exoplanetesimals could end
up being connected to the CQV phenomenon, for instance as a possible
sources for the occulting dust or gas.
However for the time being, none of the CQVs that we have
studied in this work show clear evidence for this type of
origin scenario.

@@

\begin{figure}[!t]
	\begin{center}
		\centering
		%\includegraphics[width=0.9\textwidth]{f8.pdf}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f8a.pdf}
		}

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f8b.pdf}
		}
		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection.}  HD~37776 and HD~64740 (left column) are
      magnetic B stars with field geometries dominated by high order
      multipoles.
			Here, we compare their phased TESS light curves against the
			``best-matching'' CQV light curves (right column), selected by eye from
			Figure~\ref{fig:cqvs}.
      Stellar masses rounded to one significant figure are given
      in the lower right of each panel; the star, TESS sector, and
      period are listed in the title.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

An argument against the connection between CQVs and the
$\sigma$~Ori~E analogs is that the light curve of $\sigma$~Ori~E is
much simpler than those in Figure~\ref{fig:cqvs}, with only two broad
local minima, and one ``hump'' \citep{2005ApJ...630L..81T}.  Within
the model proposed by Townsend et al., this is explained by the simplicity of the star's
magnetic field, which to first-order is a
dipole, similar to most other magnetic B stars
\citep{2009ARA&A..47..333D}.  This approximation matches the qualitative
behavior of both the broadband light curves, and the
line-profile variations seen in hydrogen, helium, and carbon
\citep{2012MNRAS.419..959O}.

Two exceptions to the rule of ``simple field topologies for magnetic
B stars'' are HD~37776 and HD~64740, which are B stars that were
previously known from spectropolarimetry in the 2000s-2010s to have
field geometries dominated by high order multipoles
\citep{2011ApJ...726...24K}.  In a review of the literature, we
learned that recent TESS light curves of these two B stars appear
surprisingly similar to the CQV light curves
\citep{2020pase.conf...46M}.  Figure~\ref{fig:bstar} shows the phased
TESS light curves for the two outlying magnetic B stars, with by-eye
``best matching'' CQVs shown for comparison.  The number of dips per
cycle, the shapes of the dips, and the dip depths relative to the
sinusoidal envelope, all seem to be quite similar.  If this connection
is taken seriously, the implication would be that the
highly-structured M dwarf light curves imply multipolar magnetic
fields -- since it is the complex fields which are the defining
characteristic of these two B stars, relative to other known magnetic
B stars like $\sigma$~Ori~E.  
This is consistent with the non-axisymmetric topologies that have been
reported in a small number of M dwarfs for which Zeeman Doppler
Imaging is technically feasible 
\citep[see the review by][]{2021A&ARv..29....1K}.

The physical similarity between the B stars and the M dwarfs 
presumably has its origin in the existence of a ``centrifugal magnetosphere'' \citep[see][]{2013MNRAS.429..398P}.
In other
words, both classes of objects probably satisfy the condition $R_{\rm A} > R_{\rm cr}$, for
$R_{\rm A}$ the Alfv\'en radius.
When this condition holds, stable points exist wherever the outward
centrifugal force is balanced by magnetic tension of closed field loops.
In the converse ``dynamical'' case, when  $R_{\rm A} < R_{\rm cr}$, any
material launched by the star returns to its surface over the free-fall timescale.
% While there are some qualitative connections to Jupiter-Io, it's not perfect.
% In that system, R_A>R_cr...
% But the plasma torus exists near Io's 42 hour orbit
% ...and is nonetheless STILL FORCED into corotation at a 10hr period (presumably by Jupiter's B-field).
% This type of structure is very different, because here we actually see the plasma at corotation!

@@

\begin{enumerate}[leftmargin=*]
	%
	\item CQVs are quasiperiodic.  The mean periods remain fixed over the
		$>$1{,}000-cycle baseline of available observations; but the light curve shapes
		always evolve (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often but not
    exclusively linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay can also occur.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
  \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
    200\,Myr, based on the one CQV we found in the Carina Near
    moving group (TIC~294328887; $\approx$200\,Myr).  The lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    lifetime of the phenomenon is likely limited to the first few
    hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx$$75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item While the majority of detected CQVs have masses of
    0.1-0.5\,$M_\odot$, the upper mass limit for the CQV phenomenon
    might extend into the K dwarf regime ($<$$0.8$\,$M_\odot$).
    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
    $\approx$0.6 solar masses, are the two massive outliers
    (Section~\ref{subsec:extreme}), and we encourage additional
    scrutiny of these objects in future work.
  %
    \item Surprising analogs to the M  and K dwarf CQVs exist in
    magnetic B stars, but only those with multipolar field topologies.
    This suggests that the CQV dips and warps are strongly sculpted
    by the stellar magnetic fields, which are probably also multipolar.
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

{\bf DRAFT AUTHOR CONTRIBUTION STATEMENTS -- PLEASE REVISE IF 
	APPROPRIATE)}
LGB~and RJ conceived the project and executed the
dip-based and Fourier-based searches, respectively.
LGB~drafted the initial manuscript, and performed the cluster
membership, SED, and variability analyses.
SR and RJ vetted the results from the Fourier search.
LAH advised on project scope and experiment design.
AD identified the magnetic B star connection.
G\'AB acquired and maintained the servers used to run the dip-finding
pipeline.
GRR is an architect of the TESS mission.
All authors assisted in manuscript revision.
